FoRTE baseline

### 2019-03-27 analysis/paper/paper.Rmd
Expand paper outline

## library(fortebaseline) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

@@

@@

>>>>

## library(fortebaseline) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
n <- 0
mdcap <- function(text) {
  n <<- n + 1
  out <- sprintf("**Figure %d**: %s", n, text)
  if (grepl("gfm", knitr::opts_knit$get("rmarkdown.pandoc.to"), ignore.case = TRUE)) {
    out
  } else {
    invisible(NULL)
  }
}
```

# Outline

- **Introduction**
    - Why we need models?
        - Forests are important, for C sequestration, other ecosystem services
        - Policy decisions related to forests depend on future projections
        - We need models to make future projections
    - What kinds of models are out there?
        - Traditional: "Big leaf" models
            - Needed to be simple to run on old computers
            - Don't need as much data
            - ...but they fail to capture important processes, which matter not only for accurate predictions about C cycle, but also because they are processes we care about (habitat, forestry, tourism, etc.)!
        - Individual-based models
            - Much more detailed, but harder to run, and need much more data.
            - Trade-off between complexity and accuracy.
        - Cohort-based models like ED2 as a middle ground?
    - How much complexity do we need to accurately model ecological succession?
        - Lots of existing work on parameteric uncertainty (e.g. Dietze, Raczka, others).
        - Less on structural uncertainty -- i.e. not just what coefficients do we use, but what _equations_, and more generally, what _processes_ do we even consider?
    - What are the processes that drive succession of ecological communities?
        - Competition for light
        - Competition for nutrients
        - Competition for water?
        - Others?
        - Brief review of community/ecosystem ecology of the Upper Midwest
    - Guiding questions:
        - Which of these processes do we need to be able to accurately model what happens ("community succession and C cycle dynamics") to Midwestern forests?
        - What is the cost of considering these processes, in terms of additional parameteric uncertainty?
        - What are the relative contributions of parameteric uncertainty (data limitation) vs. structural uncertainty (theoretical limitation?)?
    - Study overview:
        - ED with factorial combination of submodels
        - Ensemble analysis to look at parameter uncertainty
- **Methods**
    - Site description
    - ED2 model description
        - Common features
        - Submodel descriptions (in brief; more details in appendices)
            - Two-stream RTM
            - Multiple-scatter RTM
            - Finite canopy radius model
            - Trait plasticity scheme
            - N limitation (?)
    - Data sources
        - TRY data
        - Other data? FIA? Remote sensing?
    - Modeling workflow (PEcAn, etc.)
    - Data analysis
        - Structural vs. parametric uncertainty
        - Comparison against "reality"
- **Results**
    - Summary:
        - LAI time series with uncertainties, faceted by model structure
    - Structural uncertainty details
        - Understory light environment and how it affects species matters
        - The multiple-scatter
            - Fig: RTM comparison (Radiation profile)
            - Fig: Crown model comparison
            - Fig: Trait plasticity?
    - Uncertainty analysis
        - Which parameters contribute the most uncertainty?
        - Structural vs. parameteric uncertainty
- **Discussion**
    - Ecological implications of structural uncertainty
        - Predictions about ecological succession are very sensitive to the understory light environment.
            - Need a good representation of canopy structure (finite canopy radius)
            - How you model canopy radiative transfer matters! Small differences in the model can give significant results.
        - But, trait plasticity can provide an alternative mechanism for success in the understory.
            - Important modeling implication for all the emerging research on intra-specific trait variability.
            - This combination of discrete functional types with plastic traits is closer to reality than purely trait-based ("eco-evolutionary?") models or completely discretized models with static traits on the other.
            - Important caveat: Current implementation is based entirely on tropical data, which has more extreme canopy shading than temperate forests (REF), so tropical species may have evolved stronger trait plasticity than temperate species (REF).
    - Implications of uncertainty analysis for future data collection and model development
        - Parameter uncertainty is still a _huge_ source of overall model predictive uncertainty. Different parameters can give _qualitatively_ different ecological outcomes.
        - Looking beyond aggregate variables (e.g. net primary productivity, total LAI) is essential to model evaluation and calibration. It's possible to generate a relatively?
        - (Expected) Subsurface parameters (e.g. leaf-root ratios) have high sensitivity, but are poorly constrained.
        - Trait covariance may alleviate some data limitation (Shiklomanov et al. 2018 [preprint])
    - Future directions: Predicting disturbance response

@@

`r mdcap(lai_10yr_cap)`

@@

`r mdcap(rad_barplot_cap)`
